---
title: "read_data"
author: "Yongrong Chai"
date: '2022-03-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read Raw data
```{r}
library("R.matlab")

```

```{r}
data<-readMat('Raw data/GRFx.mat')
GRFx<-data$GRFx
data<-readMat('Raw data/GRFy.mat')
GRFy<-data$GRFy
data<-readMat('Raw data/GRFz.mat')
GRFz<-data$GRFz
```

```{r}
data<-readMat('Raw data/Mx.mat')
Mx<-data$Mx
data<-readMat('Raw data/My.mat')
My<-data$My
data<-readMat('Raw data/Mz.mat')
Mz<-data$Mz
```

```{R}
data<-readMat('Raw data/COPx.mat')
COPx<-data$COPx
data<-readMat('Raw data/COPy.mat')
COPy<-data$COPy
```

```{r}
data<-readMat('Raw data/AP_GRF_stance_N.mat')
AP_GRF_stance_N<-data$AP_GRF_stance_N
data<-readMat('Raw data/ML_GRF_stance_N.mat')
ML_GRF_stance_N<-data$ML_GRF_stance_N
data<-readMat('Raw data/V_GRF_stance_N.mat')
V_GRF_stance_N<-data$V_GRF_stance_N
```

```{r}
data<-readMat('Raw data/COPx_stance.mat')
COPx_stance<-data$COPx_stance
data<-readMat('Raw data/COPy_stance.mat')
COPy_stance<-data$COPy_stance
```

```{r}
IDinfo<-read.csv("Raw data/IDinfo.csv")
discrete<-read.csv("Raw data/discrete.csv")
```

```{r}
library(ggplot2)
library(ggfortify)
pca_data1 <-cbind(IDinfo, discrete)[,c(2,5,6,7,8)]
pr_out_impulse = prcomp(pca_data1[, c(2:5)], scale = TRUE)
autoplot(pr_out_impulse, data = pca_data1,colour = 'KNEE', size = 1, label.size = 3,
         loadings = TRUE, loadings.colour = 'blue',
         loadings.label = TRUE, loadings.label.size = 3,loadings.label.colour = 'black')

pca_data2 <-cbind(IDinfo, discrete)[,c(2,12,13,15,16)]
pr_out_unloading = prcomp(pca_data2[, c(2:5)], scale = TRUE)
autoplot(pr_out_unloading, data = pca_data2,colour = 'KNEE', size = 1, label.size = 3,
         loadings = TRUE, loadings.colour = 'blue',
         loadings.label = TRUE, loadings.label.size = 3,loadings.label.colour = 'black')

pca_data3 <-cbind(IDinfo, discrete)[,c(2,18:25)]
pr_out_peak = prcomp(pca_data3[, c(2:9)], scale = TRUE)
autoplot(pr_out_peak, data = pca_data3,colour = 'KNEE', size = 1, label.size = 3,
         loadings = TRUE, loadings.colour = 'blue',
         loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = 'black')

pca_data4 <-cbind(IDinfo, discrete)[,c(2,14,17,26:33)]
pr_out_time = prcomp(pca_data4[, c(2:11)], scale = TRUE)
autoplot(pr_out_time, data = pca_data4,colour = 'KNEE', size = 1, label.size = 3,
         loadings = TRUE, loadings.colour = 'blue',
         loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = 'black')
```

```{r}
pca.time.summary<-summary(pr_out_time)
ls(pca.time.summary) # Lists the objects produced by summary
```
We are interested to know (1) what are the important factors that emerge from the PCA (i.e. which ones explain a lot of variation) and (2) what do these factors actually say about the variation observed in our data. For (1), look at the importance object in the summary:

```{r}
pca.time.summary$importance
```
The second row, Proportion of Variance, shows how much variation in the data is described by each component;
we will focus on the first 6 principal components, PC1 -- PC6, which together explain 81.971% of the observed variation.

What are the principal components actually explaining? The rotation from the summary call has the information we are interested in.
```{r}
pca.time.summary$rotation
```
？？？
Biplot
```{r}
#biplot(x = pr_out_time)
autoplot(pr_out_time, data = pca_data4,colour = 'KNEE', size = 1, label.size = 3,
         loadings = TRUE, loadings.colour = 'blue',
         loadings.label = TRUE, loadings.label.size = 3, loadings.label.colour = 'black')

plot(x = pr_out_time$x[, 1],
     y = pr_out_time$x[, 2],
     xlab = "PC 1",
     ylab = "PC 2")
```

```{r}
pca.impulse.summary<-summary(pr_out_impulse)
pca.unloading.summary<-summary(pr_out_unloading)
pca.peak.summary<-summary(pr_out_peak)


pca.impulse.summary$importance #first2 - 0.555930+0.321630
pca.unloading.summary$importance #first2 - 0.710820+0.1478000
pca.peak.summary$importance #first5 - 0.322190+0.188500+0.137390+0.1226800+0.0957700
pca.time.summary$importance #first6
```

```{r}
pca.impulse.summary$rotation #详情请见iPad
plot(x = pr_out_impulse$x[, 1],
     y = pr_out_impulse$x[, 2],
     xlab = "PC 1",
     ylab = "PC 2")
par(mfrow = c(2, 2), las = 2) 
boxplot(formula = vGRF_impulse ~ KNEE, data = pca_data1)
boxplot(formula = mGRF_impulse ~ KNEE, data = pca_data1)
boxplot(formula = lGRF_impulse ~ KNEE, data = pca_data1)
boxplot(formula = aGRF_impulse ~ KNEE, data = pca_data1)
```


RSSA:
svd.method: 
1.nutrlan 2.propack(faster & #stable): long series & large window length; TRUNCATED
3.eigen 4.svd: small series & window length;   FULL
```{r}
library(Rssa)
# Decomposition stage
s <- ssa(co2, L = 120)
# Reconstruction stage
# The results are the reconstructed series r$F1, r$F2, and r$F3
recon <- reconstruct(s, groups = list(c(1,4), c(2,3), c(5,6)))
# Calculate the residuals
res <- residuals(recon)

```

```{r}
pca_data1
pca_data2
pca_data3
pca_data4
res.pca.3 <- PCA(pca_data3[, c(2:9)], graph = FALSE)
fviz_pca_var(res.pca.3, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
)
fviz_eig(res.pca.3, addlabels = TRUE, ylim = c(0, 50)) #White Black Hispanic Asia Other North American 
fviz_cos2(res.pca.3, choice = "var", top = 5) #The cos2 values are used to estimate the quality of the representation

res.pca.4 <- PCA(pca_data4[, c(2:11)], graph = FALSE)
fviz_pca_var(res.pca.4, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             repel = TRUE # Avoid text overlapping
)
fviz_eig(res.pca.4, addlabels = TRUE, ylim = c(0, 50)) #White Black Hispanic Asia Other North American 
fviz_cos2(res.pca.4, choice = "var", top = 7)


```

```{r}
three_scaled <- scale(pca_data4[,-1])
row.names(three_scaled) <- NULL

three.ch <- hclust(dist(three_scaled), method = "ward.D")
plot(three.ch)
rect.hclust(three.ch, k = 32)

criteria <- CHCriterion(data = three_scaled, kmax = 7, 
                        clustermethod = "hclust", method = "ward.D")
criteria$plot



whole_scaled <- scale(cbind(IDinfo, discrete)[,-c(1,2)])
row.names(whole_scaled) <- NULL
criteria4 <- CHCriterion(data = whole_scaled, kmax = 31, 
                        clustermethod = "hclust", method = "ward.D")
criteria4$plot
```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```

```{r}


```









